Declarative Methods Term Project: \\ JumanG

### 2013-05-04 doc/paper.tex
Added more figures to the paper.
serp

\subsection{Radial Solver}
Radial displays have been used to display trees in a way different from a typical top-down approach.
Introduced in 1992 by Eades (EADES CITATION), this layout places the branches circularly around the root outwards, drawing 
nodes at different radii from the center. We implemented our own Radial solver that uses similar techniques to the original
method. We wrote our solver to evenly distribute nodes around the root at each level, rather than the typical style of weighting 
the nodes based on the subnodes. We also chose to display nodes at their closest level to root. 
This allows the solver to draw non-tree graphs fairly well. Here is our solver against Graphviz's twopi on some of the same graphs: 
%TODO (INSERT COMPARISON GRAPHS)

@@

\subsubsection{Springs solver's Initialization}
The Springs solver also requires the nodes to have an initial configuration. 
%TODO citation of book
suggests two possible approaches. The first being random placement, where all of the nodes are randomized, and the second being based on geodesic distance. We have implemented both options, the second option using the Radial solver as an alternative to this geodesic distance initialization.

@@

>>>>

\subsection{Radial Solver}
Radial displays have been used to display trees in a way different from a typical top-down approach.
Introduced in 1992 by Eades \cite{freeTrees}, this layout places the branches circularly around the root outwards, drawing 
nodes at different radii from the center. We implemented our own Radial solver that uses similar techniques to the original
method. We wrote our solver to evenly distribute nodes around the root at each level, rather than the typical style of weighting 
the nodes based on the subnodes. We also chose to display nodes at their closest level to root. 
This allows the solver to draw non-tree graphs fairly well. In some instances, we can even beat Graphviz's twopi instantiation, detailed below in our experimental comparison section. %TODO wording

@@

\subsubsection{Springs solver's Initialization}
The Springs solver also requires the nodes to have an initial configuration. Wilkinson \cite{grammarGraphics}
%TODO style?
suggests two possible approaches. The first being random placement, where all of the nodes are randomized, and the second being based on geodesic distance. We have implemented both options, the second option using the Radial solver as an alternative to this geodesic distance initialization.

@@

In most cases, we match Graphviz's implementation, such as in rendering a Sierpinski triangle:

\begin{figure}[h!]
\caption{GraphViz's neato solver's version of a Sierpinski triangle}
\centering
\includegraphics[width=0.3\textwidth]{serp.png}
\end{figure}

\begin{figure}
\caption{Our Spring Solver's version of the same Sierpinski triangle}
\begin{tikzpicture}[scale=0.40, transform shape]
	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
	\node (1) at (4.55, -4.87) {1};
	\node (3) at (-6.33, -1.86) {3};
	\node (2) at (1.72, 6.06) {2};
	\node (5) at (2.95, 0.54) {5};
	\node (4) at (-0.84, -3.18) {4};
	\node (6) at (-2.16, 1.96) {6};
	\draw [-] (1)--(4);
	\draw [-] (1)--(5);
	\draw [-] (3)--(4);
	\draw [-] (3)--(6);
	\draw [-] (2)--(5);
	\draw [-] (2)--(6);
	\draw [-] (5)--(1);
	\draw [-] (5)--(2);
	\draw [-] (5)--(4);
	\draw [-] (5)--(6);
	\draw [-] (4)--(1);
	\draw [-] (4)--(3);
	\draw [-] (4)--(5);
	\draw [-] (4)--(6);
	\draw [-] (6)--(2);
	\draw [-] (6)--(3);
	\draw [-] (6)--(4);
	\draw [-] (6)--(5);
\end{tikzpicture}

In some cases, we can even beat GraphViz's performance by a small margin:

\begin{figure}[h!]
\caption{GraphViz's 2Pi Radial Solver's version of an example graph}
\centering
\includegraphics[width=0.3\textwidth]{turnip_dag.png}
\end{figure}

\begin{figure}
\caption{Our Radial Solver's version of the example graph. Compared to 2Pi.}
\begin{tikzpicture}[scale=0.70, transform shape]
	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
	\node (Steve) at (0.00, 0.00) {Steve};
	\node (Louis) at (0.00, -3.00) {Louis};
	\node (Katrina) at (-4.24, 4.24) {Katrina};
	\node (Danielle) at (0.00, 3.00) {Danielle};
	\node (Vivian) at (4.24, 4.24) {Vivian};
	\draw [->] (Steve)--(Danielle);
	\draw [->] (Steve)--(Louis);
	\draw [->] (Danielle)--(Vivian);
	\draw [->] (Danielle)--(Katrina);
	\draw [->] (Vivian)--(Katrina);
\end{tikzpicture}
\end{figure}
